Misspecification Demonstration

### 2022-08-12 misspecification_study/misspec_demo.Rmd
knit with Tim's sim fix, osa fix still needed
make some minor edits to misspec_demo.Rmd

obs_names = c("agg_indices","agg_catch","catch_paa","index_paa", "Ecov_obs", "obsvec")

# sim_input[[1]] has no data modification and em1
set.seed(14159265) #use same seed for all operating models
sim_input[[1]] = lapply(1:nsim, function(x) {
  input_i = em_input1
  sim = om$simulate(complete=TRUE)
  input_i$data[obs_names] = sim[obs_names]
  return(input_i)
})

# sim_input[[2]] uses the correct data and em2
sim_input[[2]] = lapply(1:nsim, function(x) {
  input_i = em_input2
  input_i$data[obs_names] = sim_input[[1]][[x]]$data[obs_names]
  return(input_i)
})

# sim_input[[3]] uses the correct data and em3
sim_input[[3]] = lapply(1:nsim, function(x) {
  input_i = em_input3
  input_i$data[obs_names] = sim_input[[1]][[x]]$data[obs_names]
  return(input_i)
})

# sim_input[[4]] uses the correct data and em4
sim_input[[4]] = lapply(1:nsim, function(x) {
  input_i = em_input4
  input_i$data[obs_names] = sim_input[[1]][[x]]$data[obs_names]
  return(input_i)
})

# now create the under-reported catch data
# sim_input[[5]] has under-reported catch and em1
set.seed(14159265) #use same seed for all operating models
agg_catch_multiplier <- create_agg_catch_multiplier(input, multiplier=0.33)
sim_input[[5]] = lapply(1:nsim, function(x) {
  input_i = em_input1
  sim = om$simulate(complete=TRUE)
  sim <- bias_data(sim, multiply_agg_catch_flag=TRUE,
                   agg_catch_multiplier=agg_catch_multiplier)
  input_i$data = sim
  return(input_i)
})

# sim_input[[6]] has under-reported catch and em2
sim_input[[6]] = lapply(1:nsim, function(x) {
  input_i = em_input2
  input_i$data[obs_names] = sim_input[[5]][[x]]$data[obs_names]
  return(input_i)
})

# sim_input[[7]] has under-reported catch and em3
sim_input[[7]] = lapply(1:nsim, function(x) {
  input_i = em_input3
  input_i$data[obs_names] = sim_input[[5]][[x]]$data[obs_names]
  return(input_i)
})

# sim_input[[8]] has under-reported catch and em4
sim_input[[8]] = lapply(1:nsim, function(x) {
  input_i = em_input4
  input_i$data[obs_names] = sim_input[[5]][[x]]$data[obs_names]
  return(input_i)
})
```

>>>>

obs_names = c("agg_indices","agg_catch","catch_paa","index_paa", "Ecov_obs", "obsvec", "agesvec")

# sim_input[[1]] has no data modification and em1
set.seed(14159265) #use same seed for all operating models
sim_input[[1]] = lapply(1:nsim, function(x) {
  input_i = em_input1
  sim = om$simulate(complete=TRUE)
  input_i$data[obs_names] = sim[obs_names]
  input_i$data$obs$val = input_i$data$obsvec
  return(input_i)
})

# sim_input[[2]] uses the correct data and em2
sim_input[[2]] = lapply(1:nsim, function(x) {
  input_i = em_input2
  input_i$data[obs_names] = sim_input[[1]][[x]]$data[obs_names]
  input_i$data$obs$val = input_i$data$obsvec
  return(input_i)
})

# sim_input[[3]] uses the correct data and em3
sim_input[[3]] = lapply(1:nsim, function(x) {
  input_i = em_input3
  input_i$data[obs_names] = sim_input[[1]][[x]]$data[obs_names]
  input_i$data$obs$val = input_i$data$obsvec
  return(input_i)
})

# sim_input[[4]] uses the correct data and em4
sim_input[[4]] = lapply(1:nsim, function(x) {
  input_i = em_input4
  input_i$data[obs_names] = sim_input[[1]][[x]]$data[obs_names]
  input_i$data$obs$val = input_i$data$obsvec
  return(input_i)
})

# now create the under-reported catch data
# sim_input[[5]] has under-reported catch and em1
set.seed(14159265) #use same seed for all operating models
agg_catch_multiplier <- create_agg_catch_multiplier(input, multiplier=0.33)
sim_input[[5]] = lapply(1:nsim, function(x) {
  input_i = em_input1
  sim = om$simulate(complete=TRUE)
  sim <- bias_data(sim, multiply_agg_catch_flag=TRUE,
                   agg_catch_multiplier=agg_catch_multiplier)
  input_i$data[obs_names] = sim[obs_names]
  input_i$data$obs$val = input_i$data$obsvec
  return(input_i)
})

# sim_input[[6]] has under-reported catch and em2
sim_input[[6]] = lapply(1:nsim, function(x) {
  input_i = em_input2
  input_i$data[obs_names] = sim_input[[5]][[x]]$data[obs_names]
  input_i$data$obs$val = input_i$data$obsvec
  return(input_i)
})

# sim_input[[7]] has under-reported catch and em3
sim_input[[7]] = lapply(1:nsim, function(x) {
  input_i = em_input3
  input_i$data[obs_names] = sim_input[[5]][[x]]$data[obs_names]
  input_i$data$obs$val = input_i$data$obsvec
  return(input_i)
})

# sim_input[[8]] has under-reported catch and em4
sim_input[[8]] = lapply(1:nsim, function(x) {
  input_i = em_input4
  input_i$data[obs_names] = sim_input[[5]][[x]]$data[obs_names]
  input_i$data$obs$val = input_i$data$obsvec
  return(input_i)
})
```
